Brief notes on erosion

### 2020-08-25 docs/proposals/NSF/budgets/budgetJustUSNA.tex
NM

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection*{A: Senior Personnel (co-PI: Matthew Moore)}
%\hfill \\
%\noindent
The requested senior personnel funding is to support one month of 
co-PI Moore's summer salary in each of years 1--3. During this period, the PIs
will work together to develop and implement algorithms, write papers,
and work closely with the graduate student. 
Co-PI Moore's salary will in years 1,2,3 will be USNA Step 30, 31, and 32 respectively, with the monthly salaries listed in the table:
%\hfill \\
\begin{center}
  \begin{tabular}{|c|r|r|r|r|}
    \hline
    & Year 1 & Year 2 & Year 3  & Total \\
    \hline
    co-PI Moore & $\$9,584.61$ & $\$9,762.27$ & $\$9,977.10$  & $\$29,323.98$ \\
    \hline
  \end{tabular}
\end{center}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection*{C: Fringe Benefits}
The fringe benefits of co-PI Moore at USNA are 34\%. 
In addition a COLA of 3\% is added: \\
%\hfill \\
\begin{center}
  \begin{tabular}{|c|r|r|r|r|}
    \hline
    & Year 1 & Year 2 & Year 3 & Total \\
    \hline
    co-PI Moore Fringe & $\$3,258.77$ & $\$3,319.17$ & $\$3,392.21$ & $\$9,970.15$ \\
    \hline
    co-PI Moore COLA & $\$287.54$ & $\$292.87$ & $\$299.31$ & $\$879.72$ \\
    \hline
    Total & $\$3,546.31$ & $\$3,612.04$ & $\$3,691.52 $ & $\$10,849.85
$ \\
    \hline
  \end{tabular}
\end{center}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection*{H: Total Direct Costs}
%\hfill \\
%\noindent
Total of Sections A--G.
%\hfill \\
\begin{center}
  \begin{tabular}{|c|c|c|c|}
    \hline
    Year 1 & Year 2 & Year 3 & Total \\
    \hline
    $\$14,130.92$ & $\$14,374.31$ & $\$14,668.63$ & $\$43,173.86
$ \\
    \hline
  \end{tabular}
\end{center}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection*{I: Indirect Costs}
%\hfill \\
%\noindent
The US Naval Academy's federally negotiated indirect cost rate is
10\% for research on modified total direct costs (MTDC).
The base for overhead is $\$14,130.92$ in year 1, $\$14,374.31$ in
year 2, and $\$14,668.63$ in year 3.
%\hfill \\
\begin{center}
  \begin{tabular}{|c|c|c|c|}
    \hline
    Year 1 & Year 2 & Year 3 & Total \\
    \hline
    $\$1,413.09$ & $\$1,437.43$ & $\$1,466.86$ & $\$4,317.38$ \\
    \hline
  \end{tabular}
\end{center}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection*{J: Total Direct and Indirect Costs}
%\hfill \\
%\noindent
Total of Sections H and I.
%\hfill \\
\begin{center}
  \begin{tabular}{|c|c|c|c|}
    \hline
    Year 1 & Year 2 & Year 3 & Total \\
    \hline
    $\$15,544.01$ & $\$15,811.74$ & $\$16,135.49$ & $\$47,491.24$ \\
    \hline
  \end{tabular}
\end{center}

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection*{A: Senior Personnel (co-PI: Matthew Moore)}
%\hfill \\
%\noindent
The requested senior personnel funding is to support one month of 
co-PI Moore's summer salary in each of years 1--3. During this period, the PIs
will work together to develop and implement algorithms, write papers,
and work closely with the graduate student. 
Co-PI Moore's salary will in years 1,2,3 will be USNA Step 30, 31, and 32 respectively, with the monthly salaries listed in the table:
%\hfill \\
\begin{center}
  \begin{tabular}{|c|r|r|r|r|}
    \hline
    & Year 1 & Year 2 & Year 3  & Total \\
    \hline
    co-PI Moore & $\$9,585$ & $\$9,762$ & $\$9,977$  & $\$29,324$ \\
    \hline
  \end{tabular}
\end{center}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection*{C: Fringe Benefits}
The fringe benefits of co-PI Moore at USNA are 34\%. 
In addition a COLA of 3\% is added to estimate the cost of living increase government works may receive in January. \\
%\hfill \\
\begin{center}
  \begin{tabular}{|c|r|r|r|r|}
    \hline
    & Year 1 & Year 2 & Year 3 & Total \\
    \hline
    co-PI Moore Fringe & $\$3,259$ & $\$3,319$ & $\$3,392$ & $\$9,970$ \\
    \hline
    co-PI Moore COLA & $\$288$ & $\$293$ & $\$299$ & $\$880$ \\
    \hline
    Total & $\$3,546$ & $\$3,612$ & $\$3,692$ & $\$10,850$ \\
    \hline
  \end{tabular}
\end{center}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection*{H: Total Direct Costs}
%\hfill \\
%\noindent
Total of Sections A--G.
%\hfill \\
\begin{center}
  \begin{tabular}{|c|c|c|c|}
    \hline
    Year 1 & Year 2 & Year 3 & Total \\
    \hline
    $\$14,130.92$ & $\$14,374$ & $\$14,669$ & $\$43,174$ \\
    \hline
  \end{tabular}
\end{center}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection*{I: Indirect Costs}
%\hfill \\
%\noindent
The US Naval Academy's indirect cost rate is
10\% for research on modified total direct costs (MTDC).
The base for overhead is $\$14,130.92$ in year 1, $\$14,374.31$ in
year 2, and $\$14,668.63$ in year 3.
The US Naval Academy defines a fiscal year to be July 1-June 30.
%\hfill \\
\begin{center}
  \begin{tabular}{|c|c|c|c|}
    \hline
    Year 1 & Year 2 & Year 3 & Total \\
    \hline
    $\$1,413$ & $\$1,437$ & $\$1,467$ & $\$4,317$ \\
    \hline
  \end{tabular}
\end{center}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection*{J: Total Direct and Indirect Costs}
%\hfill \\
%\noindent
Total of Sections H and I.
%\hfill \\
\begin{center}
  \begin{tabular}{|c|c|c|c|}
    \hline
    Year 1 & Year 2 & Year 3 & Total \\
    \hline
    $\$15,544$ & $\$15,812$ & $\$16,135$ & $\$47,491$ \\
    \hline
  \end{tabular}
\end{center}
